Title

### 2018-09-01 thesis/paper/paper.tex
Renamed Link to Citation Needed

\begin{table}[H]
\caption{property constraints}\label{tab_property_constraints}
\begin{tabularx}{\textheight}{rlll}
\makecell{\# constrained\\ properties} & Identifier & Name & Required Features \\
\hline
1410 & Q53869507 & Scope &  \\
781 & Q21502838 & Conflicts with &  \\
27 & Q52004125 & Allowed entity types &  \\
17 & Q52558054 & None of &  \\
\hline
2843 & Q21502410 & Distinct value & Inequality \\
343 & Q21514353 & Allowed units & Inequality \\
303 & Q21510851 & Allowed qualifiers & Inequality \\
116 & Q21510859 & One of & Inequality \\
3 & Q52060874 & Single best value & Inequality \\
1 & Q52712340 & One-of qualifier value & Inequality \\
\hline
4265 & Q21503247 & Item requires statement & Negation (statement non-existence) \\
244 & Q21510864 & Value requires statement & Negation (statement non-existence) \\
119 & Q21510855 & Inverse & Negation (statement non-existence) \\
33 & Q21510862 & Symmetric & Negation (statement non-existence) \\
13 & Q21510857 & Multi-value & Negation, Count (up to two) \\
2909 & Q19474404 & Single value & Inequality, Negation (qualifier non-existence) \\
203 & Q21510856 & Mandatory qualifier & Negation (qualifier non-existence) \\
\hline
2613 & Q21503250 & Type & Negation (derived fact negation) \\
707 & Q21510865 & Value type & Negation (derived fact negation) \\
3021 & Q21502404 & Format & Regular expressions \\
188 & Q21510860 & Range & Value comparison \\
106 & Q52848401 & Integer & Regular expressions \\
65 & Q51723761 & No bounds & Negation \\
53 & Q21510852 & Commons link & Web request \\
10 & Q54554025 & Link & Negation \\
6 & Q21510854 & Difference within range & Value comparison \\
1 & Q25796498 & Contemporary constraint & Negation \\
\end{tabularx}
\end{table}

@@

\emph{Link} constraint (Q54554025), stating that constraint statements must have one or more references, requires a negation that cannot be concluded except by explicitly precomputing it, which makes the evaluation unnecessary. \\
A similar situation is the \emph{no bounds} constraint (Q51723761), which requires that quantity values have neither upper nor lower bound. While it would be possible to precompute if a statement has no upper or lower bound, this would shift basically all evaluation logic into precomputing.

>>>>

\begin{table}[H]
\caption{property constraints}\label{tab_property_constraints}
\begin{tabularx}{\textheight}{rlll}
\makecell{\# constrained\\ properties} & Identifier & Name & Required Features \\
\hline
1410 & Q53869507 & Scope &  \\
781 & Q21502838 & Conflicts with &  \\
27 & Q52004125 & Allowed entity types &  \\
17 & Q52558054 & None of &  \\
\hline
2843 & Q21502410 & Distinct value & Inequality \\
343 & Q21514353 & Allowed units & Inequality \\
303 & Q21510851 & Allowed qualifiers & Inequality \\
116 & Q21510859 & One of & Inequality \\
3 & Q52060874 & Single best value & Inequality \\
1 & Q52712340 & One-of qualifier value & Inequality \\
\hline
4265 & Q21503247 & Item requires statement & Negation (statement non-existence) \\
244 & Q21510864 & Value requires statement & Negation (statement non-existence) \\
119 & Q21510855 & Inverse & Negation (statement non-existence) \\
33 & Q21510862 & Symmetric & Negation (statement non-existence) \\
13 & Q21510857 & Multi-value & Negation, Count (up to two) \\
2909 & Q19474404 & Single value & Inequality, Negation (qualifier non-existence) \\
203 & Q21510856 & Mandatory qualifier & Negation (qualifier non-existence) \\
\hline
2613 & Q21503250 & Type & Negation (derived fact negation) \\
707 & Q21510865 & Value type & Negation (derived fact negation) \\
3021 & Q21502404 & Format & Regular expressions \\
188 & Q21510860 & Range & Value comparison \\
106 & Q52848401 & Integer & Regular expressions \\
65 & Q51723761 & No bounds & Negation \\
53 & Q21510852 & Commons link & Web request \\
10 & Q54554025 & Citation needed & Negation \\
6 & Q21510854 & Difference within range & Value comparison \\
1 & Q25796498 & Contemporary constraint & Negation \\
\end{tabularx}
\end{table}

@@

\emph{Citation needed} constraint (Q54554025), stating that constraint statements must have one or more references, requires a negation that cannot be concluded except by explicitly precomputing it, which makes the evaluation unnecessary. \\
A similar situation is the \emph{no bounds} constraint (Q51723761), which requires that quantity values have neither upper nor lower bound. While it would be possible to precompute if a statement has no upper or lower bound, this would shift basically all evaluation logic into precomputing.
